Comprehensive quality - aware Automated Semantic Web Service Composition

### 2016-11-03 paper.tex
update
,….

\section{QoS-aware Semantic Automated Web Service Composition}\label{qswsc_approach}
\begin{figure}[h]
\centerline{
\fbox{
\includegraphics[width=12cm]{overview.pdf}}}
 \caption{Overview of the proposed approach.}
 \label{overview}
\end{figure}
In this paper, we propose a comprehensive quality model for automated semantic service composition, and optimise both the quality of semantic matchmaking and QoS. PSO has shown its efficiency in solving combinatorial optimisation problems. Therefore, we will employ a PSO-based approach, which is considered to be simple and efficient without penalising or repairing comparing to GP \cite{da2014graph}. Fig. \ref{overview} shows the overview of our approach with five steps. Step 1: The composite process is triggered by a composite goal defined in Subsection \ref{problemDes}, which describes customers requirements both functional and non-functional. A functional requirement is defined as $F(T_{Input}, T_{Output})$ , and a nonfunctional one is users' accepted level of QoS. Step 2: Those requirements are used to discover all relevant web services, which leads to a shrunken service repository that further used by PSO as a searching space. Step 3: A weighted graph representation is randomly built up interleaving with semantic matchmaking process, where web services are discovered as graph vertices while edges are assigned with semantic matchmaking quality as weights. Step 4,5: The selection of web services performs PSO algorithm in Sect. \ref{pso_algorithm} to find best particle location. Overall, this approach is different from \cite{da2016particle}, as we use weighted graphs as particle presentation while considering a comprehensive quality.

\subsection{Semantic matchmaking} \label{semantic_matchmaking}
To perform semantic matchmaking, we transfer a function match between $S_{1}: S_{output} \in C_{1}$ and $S_{2}:S_{output} \in S_{b}$ to a pair of concept match in \ref{semantic Web service Discovery}. The matching process attempts to determine semantic matching between the source concepts of $C_{1}$ and the target concepts of $C_{2}$. Meanwhile, the quality of matched concepts are calculated in the mode model in subSection \ref{qualityModel}. The purpose of semantic matchmaking is to find more component services that could also potentially satisfies the quality of QoS with considering its functional quality.

@@

\subsection{Comprehensive quality model and aggregation matrix}\label{qualityModel}
In this paper, we propose a comprehensive quality model to evaluate the overall quality of semantic web service composition. This model overcome the disadvantages of current prevailing QoS-aware optimisation, in which quality of semantic matchmaking are not considered \cite{bansal2016generalized,mier2015integrated,da2016particle,da2015graphevol,yu2013adaptive}.

@@

@@

\section{Results and Analysis}\label{results_analysis}
\subsection{Comparision Test}\label{comparisionTest}
\begin{figure}[h]
\centerline{
\fbox{
\includegraphics[width=8cm]{wscs.pdf}}}
 \caption{Example composition solutions for problem1 WSC'09.}
 \label{wscs}
\end{figure}
We defined our optimised web service composition as $WSC = (V, E)Graph$, where $V$ is a set of services as vertex: $V=[S1, S2...Sn]$ and $E$ is a set of service connections as edges associated with two values of matchType quality and semantic similarity quality: $E = {e_{1}, e_{2},... e_{n}}$ where $e1$ is define as $(S_{1},S_{2})={q_{mt}, q_{s}}$. Here we provide an example of the web service composition solution to task 1, which can be described in the Figure \ref{wscs}. The data of composite web service flows from the start to the end, where five web services involved and linked with each other using edge connections. Besides that, $q(s_{mt})$ and $q(s_{s})$ are calculated for all edges ${e_{1}, e_{2},... e_{n}}$, and further aggregated in $Q_{mt}$ and $Q_{s}$ respectively. In addition, $Q_{QoS}$ is calculated by all the non-functional attributes of $V$ using aggregation rules defined before. The demonstration of the solution is to make better comparison of results using the same solution model from different approaches .

>>>>

\section{Comprehensive quality-aware Semantic Automated Web Service Composition}\label{qswsc_approach}
\begin{figure}[h]
\centerline{
\fbox{
\includegraphics[width=12cm]{overview.pdf}}}
 \caption{Overview of the proposed approach.}
 \label{overview}
\end{figure}
In this paper, we propose a comprehensive quality model for automated semantic service composition, and optimise both the quality of semantic matchmaking and QoS. PSO has shown its efficiency in solving combinatorial optimisation problems. Therefore, we will employ a PSO-based approach, which is considered to be simple and efficient without penalising or repairing comparing to GP \cite{da2014graph}. Fig. \ref{overview} shows the overview of our approach with five steps. Step 1: The composite process is triggered by a composite goal defined in Subsection \ref{problemDes}, which describes customers requirements both functional and non-functional. A functional requirement is defined as $F(T_{Input}, T_{Output})$ , and a nonfunctional one is users' accepted level of QoS. Step 2: Those requirements are used to discover all relevant web services, which leads to a shrunken service repository that further used by PSO as a searching space. Step 3: A weighted graph representation is randomly built up interleaving with semantic matchmaking process, where web services are discovered as graph vertices while edges are assigned with semantic matchmaking quality as weights. Step 4,5: The selection of web services performs PSO algorithm in Sect. \ref{pso_algorithm} to find best particle location. Overall, this approach is different from \cite{da2016particle}, as we use weighted graphs as particle presentation while considering a comprehensive quality.

\subsection{Semantic Matchmaking} \label{semantic_matchmaking}
To perform semantic matchmaking, we transfer a function match between $S_{1}: S_{output} \in C_{1}$ and $S_{2}:S_{output} \in S_{b}$ to a pair of concept match in \ref{semantic Web service Discovery}. The matching process attempts to determine semantic matching between the source concepts of $C_{1}$ and the target concepts of $C_{2}$. Meanwhile, the quality of matched concepts are calculated in the mode model in subSection \ref{qualityModel}. The purpose of semantic matchmaking is to find more component services that could also potentially satisfies the quality of QoS with considering its functional quality.

@@

\subsection{Comprehensive Quality Model and Aggregation Matrix}\label{qualityModel}
In this paper, we propose a comprehensive quality model to evaluate the overall quality of semantic web service composition. This model overcome the disadvantages of current prevailing QoS-aware optimisation, in which quality of semantic matchmaking are not considered \cite{bansal2016generalized,mier2015integrated,da2016particle,da2015graphevol,yu2013adaptive}.

@@

\subsection{Composition Weighted Graph}
We defined our semantic web service composition solution as $WG = (V, E)Graph$, where $V$ is a set of services as vertex: $V=[S1, S2...Sn]$ and $E$ is a set of edges $E = {e_{1}, e_{2},... e_{n}}$. Each $e$ is associated with $q(e_{sm})$ as weight value that mapped to a pair of quality values $q(e_{mt})$ and $q(e_{s})$ on the edge level. where $e_{m}$ is expressed as $(S_{a},S_{b})={q_{mt}, q_{s}}$. Here we provide an example of the web service composition, which can be described in the Figure \ref{wscs}. The data of composite web service flows from the start to the end, where five web services involved and linked with each other using edge connections. Besides that, $q(s_{mt})$ and $q(s_{s})$ are calculated for all edges ${e_{1}, e_{2},... e_{n}}$, and further aggregated in $Q_{mt}$ and $Q_{s}$ respectively on the construct level. In addition, $Q_{QoS}$ is calculated by all the non-functional attributes of $V$ using aggregation rules defined previously.

\begin{figure}[h]
\centerline{
\fbox{
\includegraphics[width=8cm]{weigtedGraphExample.pdf}}}
 \caption{Composition weighted graph solution}
 \label{wscs}
\end{figure}

@@

\section{Results and Analysis}\label{results_analysis}
\subsection{Comparision Test}\label{comparisionTest}

In this section, we analyse the composition solution generated by using our approach. In particularly, we show that our proposed approach can produce solutions that results better matchmaking , which meets user's goal better.
